---
title: "Figure 1 Paper HRDness"
author: "Alicia Pliego"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    number_sections: true
    theme: sandstone
---
<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
library(CINmetrics)
library(TCGAbiolinks)
library(heatmaply)
library(GenomicRanges)
library(AnnotationHub)
library(pd.genomewidesnp.6)
library(rtracklayer)
library(biovizBase) #needed for stain information
library(CINdex)
library(IRanges)
library(TxDb.Hsapiens.UCSC.hg18.knownGene)
library(Homo.sapiens)
library(DT)
library(plotly)
```


# HRDness 


```{r, echo=FALSE, warning=FALSE, message=FALSE}

df_sarcoma_dv = read.csv('/Users/aliciapliego/Projects/HRDsarcoma/data/HRD_results_subgroupsSarcoma.tsv', sep = '\t', header= TRUE)
```

HRD scores (TAI, LST and LOH) were computed using the R package (scarHRD) on the publicly available data from allele specific copy numbers from the TCGA consortium. 


## TCGA LOH in sarcoma
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
colors <- c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00" ,"#CAB2D6", "#6A3D9A" ,"#FFFF99", "#B15928")
fig <- plot_ly(df_sarcoma_dv, y = ~LOH, color = ~Type, colors= colors, type = "box",  text = df_sarcoma_dv$Case_ID, notched=TRUE) %>%
layout(
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45), yaxis = list( range = c(0,40))
)

fig
```

## TCGA LST in sarcoma
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
fig <- plot_ly(df_sarcoma_dv, y = ~LST, color = ~Type, type = "box",colors= colors,  text = df_sarcoma_dv$Case_ID, notched=TRUE) %>%
layout(
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'),tickangle = -45), yaxis = list( range = c(0,40))
)


fig
```

## TCGA TAI in sarcoma
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
fig <- plot_ly(df_sarcoma_dv, y = ~TAI, color = ~Type, type = "box", colors= colors, text = df_sarcoma_dv$Case_ID, notched=TRUE) %>%
layout(
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'),tickangle = -45), yaxis = list( range = c(0,40))

)

fig
```

## TCGA HRDscore in sarcoma
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
fig <- plot_ly(df_sarcoma_dv, y = ~HRDscore, color = ~Type, type = "box", colors= colors, text = df_sarcoma_dv$Case_ID, notched=TRUE) %>%
layout(
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45)
)

fig
```

# CINdex

Data has been scaled grouped by sarcoma type, divided by the number of cases by sarcoma type and scaled by columns.

## Heatmap

```{r , include=FALSE, echo=FALSE, message=FALSE}
#Edit results in python and annotate them and add files back here
cindex_results_sum_sarc_grp_tmr <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/cindex_all_v1.tsv', sep = '\t', header = TRUE, check.names = FALSE)

rownames(cindex_results_sum_sarc_grp_tmr) <- cindex_results_sum_sarc_grp_tmr$Sample.ID
cindex_results_sum_sarc_grp_tmr$Sample.ID <- NULL

cindex_results_sum_sarc_grp_tmr_meta <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/cindex_all_meta_v1.tsv', sep = '\t', header = TRUE)

cindex_results_sum_sarc_grp_scaled = scale(cindex_results_sum_sarc_grp_tmr)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
library(dplyr)
colors <- c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00" ,"#CAB2D6", "#6A3D9A" ,"#FFFF99", "#B15928")

Tumor_type = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT')
names(colors) <- Tumor_type

colors_df <- as.data.frame(colors)
colors_df$Tumor_type <- rownames(colors_df)
colors_tumor <- inner_join(colors_df,cindex_results_sum_sarc_grp_tmr_meta, by = "Tumor_type")

hrdcolors <- c("#EEA236FF","#46B8DAFF")
names(hrdcolors) <- c("High","Low")
hrdcolors_df <- as.data.frame(hrdcolors)
hrdcolors_df$HRDscore <- rownames(hrdcolors_df)

colors_tumor_hrd <- inner_join(colors_tumor,hrdcolors_df, by = "HRDscore")
#rownames(colors_tumor_hrd) <- colors_tumor_hrd$Tumor_type

list_tumor_colors <- c(colors_tumor_hrd$colors)
names(list_tumor_colors) <- colors_tumor_hrd$Tumor_type

list_hrd_colors <- c(colors_tumor_hrd$hrdcolors)
names(list_hrd_colors) <- colors_tumor_hrd$HRDscore
```

### Heatmap with boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- HeatmapAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_scaled), axis = TRUE))

Heatmap(t(cindex_results_sum_sarc_grp_scaled), 
        name = "CINscore", #title of legend
        column_title = "TCGA CINdex", row_title = "Chromosome",
        cluster_columns = TRUE,
        cluster_rows =   FALSE,
        top_annotation = ha,bottom_annotation = ha_boxplot,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

### Heatmap without boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- rowAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

#ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_tmr), axis = TRUE))

Heatmap(cindex_results_sum_sarc_grp_scaled, 
        name = "CINscore", #title of legend
        column_title = "TCGA CINdex", row_title = "",
        cluster_columns = FALSE,
        cluster_rows =   FALSE,
        right_annotation = ha,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
library(reshape)
cindex_results_sum_sarc_grp_tmr2 <- as.data.frame(cindex_results_sum_sarc_grp_tmr)
cindex_results_sum_sarc_grp_tmr2$HRDscore <- cindex_results_sum_sarc_grp_tmr_meta$HRDscore
cindex_results_sum_sarc_grp_tmr2$Tumor_type <- cindex_results_sum_sarc_grp_tmr_meta$Tumor_type
mdata <- melt(cindex_results_sum_sarc_grp_tmr2, id=c("HRDscore","Tumor_type"))
mdata$variable <- NULL

fig <- plot_ly(mdata, x =~Tumor_type, y = ~value, color = ~HRDscore,type = "box", notched=TRUE) %>%
layout(boxmode= 'group',
     yaxis = list(range=c(0,160), title = "CIN score"),
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45)
)

fig
```

# Amplifications 

```{r , include=FALSE, echo=FALSE, message=FALSE}
#Edit results in python and annotate them and add files back here
cindex_results_sum_sarc_grp_tmr <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/cindex_all_amp_v1.tsv', sep = '\t', header = TRUE, check.names = FALSE)

rownames(cindex_results_sum_sarc_grp_tmr) <- cindex_results_sum_sarc_grp_tmr$Sample.ID
cindex_results_sum_sarc_grp_tmr$Sample.ID <- NULL

cindex_results_sum_sarc_grp_tmr_meta <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/cindex_amp_meta_v1.tsv', sep = '\t', header = TRUE)

cindex_results_sum_sarc_grp_scaled = scale(cindex_results_sum_sarc_grp_tmr)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
library(dplyr)
colors <- c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00" ,"#CAB2D6", "#6A3D9A" ,"#FFFF99", "#B15928")

Tumor_type = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT')
names(colors) <- Tumor_type

colors_df <- as.data.frame(colors)
colors_df$Tumor_type <- rownames(colors_df)
colors_tumor <- inner_join(colors_df,cindex_results_sum_sarc_grp_tmr_meta, by = "Tumor_type")

hrdcolors <- c("#EEA236FF","#46B8DAFF")
names(hrdcolors) <- c("High","Low")
hrdcolors_df <- as.data.frame(hrdcolors)
hrdcolors_df$HRDscore <- rownames(hrdcolors_df)

colors_tumor_hrd <- inner_join(colors_tumor,hrdcolors_df, by = "HRDscore")
#rownames(colors_tumor_hrd) <- colors_tumor_hrd$Tumor_type

list_tumor_colors <- c(colors_tumor_hrd$colors)
names(list_tumor_colors) <- colors_tumor_hrd$Tumor_type

list_hrd_colors <- c(colors_tumor_hrd$hrdcolors)
names(list_hrd_colors) <- colors_tumor_hrd$HRDscore
```

### Heatmap with boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- HeatmapAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_scaled), axis = TRUE))

Heatmap(t(cindex_results_sum_sarc_grp_scaled), 
        name = "CINscore", #title of legend
        column_title = "TCGA Amplifications", row_title = "Chromosome",
        cluster_columns = TRUE,
        cluster_rows =   FALSE,
        top_annotation = ha,bottom_annotation = ha_boxplot,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

### Heatmap without boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- rowAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

#ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_tmr), axis = TRUE))

Heatmap(cindex_results_sum_sarc_grp_scaled, 
        name = "CINscore", #title of legend
        column_title = "TCGA Amplifications", row_title = "",
        cluster_columns = FALSE,
        cluster_rows =   FALSE,
        right_annotation = ha,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
library(reshape)
cindex_results_sum_sarc_grp_tmr2 <- as.data.frame(cindex_results_sum_sarc_grp_tmr)
cindex_results_sum_sarc_grp_tmr2$HRDscore <- cindex_results_sum_sarc_grp_tmr_meta$HRDscore
cindex_results_sum_sarc_grp_tmr2$Tumor_type <- cindex_results_sum_sarc_grp_tmr_meta$Tumor_type
mdata <- melt(cindex_results_sum_sarc_grp_tmr2, id=c("HRDscore","Tumor_type"))
mdata$variable <- NULL

fig <- plot_ly(mdata, x =~Tumor_type, y = ~value, color = ~HRDscore,type = "box", notched=TRUE) %>%
layout(boxmode= 'group',
     yaxis = list(range=c(0,160), title = "Amplifications"),
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45)
)

fig
```

# Deletions 

```{r , include=FALSE, echo=FALSE, message=FALSE}
#Edit results in python and annotate them and add files back here
cindex_results_sum_sarc_grp_tmr <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/cindex_all_del_v1.tsv', sep = '\t', header = TRUE, check.names = FALSE)

rownames(cindex_results_sum_sarc_grp_tmr) <- cindex_results_sum_sarc_grp_tmr$Sample.ID
cindex_results_sum_sarc_grp_tmr$Sample.ID <- NULL

cindex_results_sum_sarc_grp_tmr_meta <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/cindex_del_meta_v1.tsv', sep = '\t', header = TRUE)

cindex_results_sum_sarc_grp_scaled = scale(cindex_results_sum_sarc_grp_tmr)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
library(dplyr)
colors <- c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00" ,"#CAB2D6", "#6A3D9A" ,"#FFFF99", "#B15928")

Tumor_type = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT')
names(colors) <- Tumor_type

colors_df <- as.data.frame(colors)
colors_df$Tumor_type <- rownames(colors_df)
colors_tumor <- inner_join(colors_df,cindex_results_sum_sarc_grp_tmr_meta, by = "Tumor_type")

hrdcolors <- c("#EEA236FF","#46B8DAFF")
names(hrdcolors) <- c("High","Low")
hrdcolors_df <- as.data.frame(hrdcolors)
hrdcolors_df$HRDscore <- rownames(hrdcolors_df)

colors_tumor_hrd <- inner_join(colors_tumor,hrdcolors_df, by = "HRDscore")
#rownames(colors_tumor_hrd) <- colors_tumor_hrd$Tumor_type

list_tumor_colors <- c(colors_tumor_hrd$colors)
names(list_tumor_colors) <- colors_tumor_hrd$Tumor_type

list_hrd_colors <- c(colors_tumor_hrd$hrdcolors)
names(list_hrd_colors) <- colors_tumor_hrd$HRDscore
```

### Heatmap with boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- HeatmapAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_scaled), axis = TRUE))

Heatmap(t(cindex_results_sum_sarc_grp_scaled), 
        name = "CINscore", #title of legend
        column_title = "TCGA Deletions", row_title = "Chromosome",
        cluster_columns = TRUE,
        cluster_rows =   FALSE,
        top_annotation = ha,bottom_annotation = ha_boxplot,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

### Heatmap without boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- rowAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

#ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_tmr), axis = TRUE))

Heatmap(cindex_results_sum_sarc_grp_scaled, 
        name = "CINscore", #title of legend
        column_title = "TCGA Deletions", row_title = "",
        cluster_columns = FALSE,
        cluster_rows =   FALSE,
        right_annotation = ha,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
library(reshape)
cindex_results_sum_sarc_grp_tmr2 <- as.data.frame(cindex_results_sum_sarc_grp_tmr)
cindex_results_sum_sarc_grp_tmr2$HRDscore <- cindex_results_sum_sarc_grp_tmr_meta$HRDscore
cindex_results_sum_sarc_grp_tmr2$Tumor_type <- cindex_results_sum_sarc_grp_tmr_meta$Tumor_type
mdata <- melt(cindex_results_sum_sarc_grp_tmr2, id=c("HRDscore","Tumor_type"))
mdata$variable <- NULL

fig <- plot_ly(mdata, x =~Tumor_type, y = ~value, color = ~HRDscore,type = "box", notched=TRUE) %>%
layout(boxmode= 'group',
     yaxis = list(range=c(0,20), title = "Deletions"),
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45)
)

fig
```


# CINdex AP Own score
## CIN score
```{r , include=FALSE, echo=FALSE, message=FALSE}
#Edit results in python and annotate them and add files back here
cindex_results_sum_sarc_grp_tmr <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/cindex_AP_score.tsv', sep = '\t', header = TRUE, check.names = FALSE)

rownames(cindex_results_sum_sarc_grp_tmr) <- cindex_results_sum_sarc_grp_tmr$Sample.ID
cindex_results_sum_sarc_grp_tmr$Sample.ID <- NULL

cindex_results_sum_sarc_grp_tmr_meta <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/cindex_AP_score_meta.tsv', sep = '\t', header = TRUE, check.names = FALSE)

cindex_results_sum_sarc_grp_scaled = scale(cindex_results_sum_sarc_grp_tmr)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
library(dplyr)
colors <- c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00" ,"#CAB2D6", "#6A3D9A" ,"#FFFF99", "#B15928")

Tumor_type = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT')
names(colors) <- Tumor_type

colors_df <- as.data.frame(colors)
colors_df$Tumor_type <- rownames(colors_df)
colors_tumor <- inner_join(colors_df,cindex_results_sum_sarc_grp_tmr_meta, by = "Tumor_type")

hrdcolors <- c("#EEA236FF","#46B8DAFF")
names(hrdcolors) <- c("High","Low")
hrdcolors_df <- as.data.frame(hrdcolors)
hrdcolors_df$HRDscore <- rownames(hrdcolors_df)

colors_tumor_hrd <- inner_join(colors_tumor,hrdcolors_df, by = "HRDscore")
#rownames(colors_tumor_hrd) <- colors_tumor_hrd$Tumor_type

list_tumor_colors <- c(colors_tumor_hrd$colors)
names(list_tumor_colors) <- colors_tumor_hrd$Tumor_type

list_hrd_colors <- c(colors_tumor_hrd$hrdcolors)
names(list_hrd_colors) <- colors_tumor_hrd$HRDscore
```

### Heatmap with boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- HeatmapAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_scaled), axis = TRUE))

Heatmap(t(cindex_results_sum_sarc_grp_scaled), 
        name = "CINscore", #title of legend
        column_title = "TCGA CIN", row_title = "Chromosome",
        cluster_columns = TRUE,
        cluster_rows =   FALSE,
        top_annotation = ha,bottom_annotation = ha_boxplot,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

### Heatmap without boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- rowAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

#ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_tmr), axis = TRUE))

Heatmap(cindex_results_sum_sarc_grp_scaled, 
        name = "CINscore", #title of legend
        column_title = "TCGA CIN", row_title = "",
        cluster_columns = FALSE,
        cluster_rows =   FALSE,
        right_annotation = ha,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
library(reshape)
cindex_results_sum_sarc_grp_tmr2 <- as.data.frame(cindex_results_sum_sarc_grp_tmr)
cindex_results_sum_sarc_grp_tmr2$HRDscore <- cindex_results_sum_sarc_grp_tmr_meta$HRDscore
cindex_results_sum_sarc_grp_tmr2$Tumor_type <- cindex_results_sum_sarc_grp_tmr_meta$Tumor_type
mdata <- melt(cindex_results_sum_sarc_grp_tmr2, id=c("HRDscore","Tumor_type"))
mdata$variable <- NULL

fig <- plot_ly(mdata, x =~Tumor_type, y = ~value, color = ~HRDscore,type = "box", notched=TRUE) %>%
layout(boxmode= 'group',
     yaxis = list(range=c(0,35), title = "CIN"),
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45)
)

fig
```

## Amplifications 
```{r , include=FALSE, echo=FALSE, message=FALSE}
#Edit results in python and annotate them and add files back here
cindex_results_sum_sarc_grp_tmr <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/amplifications_AP.tsv', sep = '\t', header = TRUE, check.names = FALSE)

rownames(cindex_results_sum_sarc_grp_tmr) <- cindex_results_sum_sarc_grp_tmr$Sample.ID
cindex_results_sum_sarc_grp_tmr$Sample.ID <- NULL

cindex_results_sum_sarc_grp_tmr_meta <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/amplifications_AP_meta.tsv', sep = '\t', header = TRUE, check.names = FALSE)

cindex_results_sum_sarc_grp_scaled = scale(cindex_results_sum_sarc_grp_tmr)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
library(dplyr)
colors <- c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00" ,"#CAB2D6", "#6A3D9A" ,"#FFFF99", "#B15928")

Tumor_type = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT')
names(colors) <- Tumor_type

colors_df <- as.data.frame(colors)
colors_df$Tumor_type <- rownames(colors_df)
colors_tumor <- inner_join(colors_df,cindex_results_sum_sarc_grp_tmr_meta, by = "Tumor_type")

hrdcolors <- c("#EEA236FF","#46B8DAFF")
names(hrdcolors) <- c("High","Low")
hrdcolors_df <- as.data.frame(hrdcolors)
hrdcolors_df$HRDscore <- rownames(hrdcolors_df)

colors_tumor_hrd <- inner_join(colors_tumor,hrdcolors_df, by = "HRDscore")
#rownames(colors_tumor_hrd) <- colors_tumor_hrd$Tumor_type

list_tumor_colors <- c(colors_tumor_hrd$colors)
names(list_tumor_colors) <- colors_tumor_hrd$Tumor_type

list_hrd_colors <- c(colors_tumor_hrd$hrdcolors)
names(list_hrd_colors) <- colors_tumor_hrd$HRDscore
```

### Heatmap with boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- HeatmapAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_scaled), axis = TRUE))

Heatmap(t(cindex_results_sum_sarc_grp_scaled), 
        name = "CINscore", #title of legend
        column_title = "TCGA Amplifications", row_title = "Chromosome",
        cluster_columns = TRUE,
        cluster_rows =   FALSE,
        top_annotation = ha,bottom_annotation = ha_boxplot,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

### Heatmap without boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- rowAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

#ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_tmr), axis = TRUE))

Heatmap(cindex_results_sum_sarc_grp_scaled, 
        name = "CINscore", #title of legend
        column_title = "TCGA Amplifications", row_title = "",
        cluster_columns = FALSE,
        cluster_rows =   FALSE,
        right_annotation = ha,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
library(reshape)
cindex_results_sum_sarc_grp_tmr2 <- as.data.frame(cindex_results_sum_sarc_grp_tmr)
cindex_results_sum_sarc_grp_tmr2$HRDscore <- cindex_results_sum_sarc_grp_tmr_meta$HRDscore
cindex_results_sum_sarc_grp_tmr2$Tumor_type <- cindex_results_sum_sarc_grp_tmr_meta$Tumor_type
mdata <- melt(cindex_results_sum_sarc_grp_tmr2, id=c("HRDscore","Tumor_type"))
mdata$variable <- NULL

fig <- plot_ly(mdata, x =~Tumor_type, y = ~value, color = ~HRDscore,type = "box", notched=TRUE) %>%
layout(boxmode= 'group',
     yaxis = list(range=c(0,35), title = "Amplifications"),
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45)
)

fig
```

## Deletions
```{r , include=FALSE, echo=FALSE, message=FALSE}
#Edit results in python and annotate them and add files back here
cindex_results_sum_sarc_grp_tmr <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/deletions_AP.tsv', sep = '\t', header = TRUE, check.names = FALSE)

rownames(cindex_results_sum_sarc_grp_tmr) <- cindex_results_sum_sarc_grp_tmr$Sample.ID
cindex_results_sum_sarc_grp_tmr$Sample.ID <- NULL

cindex_results_sum_sarc_grp_tmr_meta <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/deletions_AP_meta.tsv', sep = '\t', header = TRUE, check.names = FALSE)

cindex_results_sum_sarc_grp_scaled = scale(cindex_results_sum_sarc_grp_tmr)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
library(dplyr)
colors <- c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00" ,"#CAB2D6", "#6A3D9A" ,"#FFFF99", "#B15928")

Tumor_type = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT')
names(colors) <- Tumor_type

colors_df <- as.data.frame(colors)
colors_df$Tumor_type <- rownames(colors_df)
colors_tumor <- inner_join(colors_df,cindex_results_sum_sarc_grp_tmr_meta, by = "Tumor_type")

hrdcolors <- c("#EEA236FF","#46B8DAFF")
names(hrdcolors) <- c("High","Low")
hrdcolors_df <- as.data.frame(hrdcolors)
hrdcolors_df$HRDscore <- rownames(hrdcolors_df)

colors_tumor_hrd <- inner_join(colors_tumor,hrdcolors_df, by = "HRDscore")
#rownames(colors_tumor_hrd) <- colors_tumor_hrd$Tumor_type

list_tumor_colors <- c(colors_tumor_hrd$colors)
names(list_tumor_colors) <- colors_tumor_hrd$Tumor_type

list_hrd_colors <- c(colors_tumor_hrd$hrdcolors)
names(list_hrd_colors) <- colors_tumor_hrd$HRDscore
```

### Heatmap with boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- HeatmapAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_scaled), axis = TRUE))

Heatmap(t(cindex_results_sum_sarc_grp_scaled), 
        name = "CINscore", #title of legend
        column_title = "TCGA Deletions", row_title = "Chromosome",
        cluster_columns = TRUE,
        cluster_rows =   FALSE,
        top_annotation = ha,bottom_annotation = ha_boxplot,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

### Heatmap without boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- rowAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

#ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_tmr), axis = TRUE))

Heatmap(cindex_results_sum_sarc_grp_scaled, 
        name = "CINscore", #title of legend
        column_title = "TCGA Deletions", row_title = "",
        cluster_columns = FALSE,
        cluster_rows =   FALSE,
        right_annotation = ha,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
library(reshape)
cindex_results_sum_sarc_grp_tmr2 <- as.data.frame(cindex_results_sum_sarc_grp_tmr)
cindex_results_sum_sarc_grp_tmr2$HRDscore <- cindex_results_sum_sarc_grp_tmr_meta$HRDscore
cindex_results_sum_sarc_grp_tmr2$Tumor_type <- cindex_results_sum_sarc_grp_tmr_meta$Tumor_type
mdata <- melt(cindex_results_sum_sarc_grp_tmr2, id=c("HRDscore","Tumor_type"))
mdata$variable <- NULL

fig <- plot_ly(mdata, x =~Tumor_type, y = ~value, color = ~HRDscore,type = "box", notched=TRUE) %>%
layout(boxmode= 'group',
     yaxis = list(range=c(0,35), title = "Deletions"),
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45)
)

fig
```


# Aneuploidies
```{r , include=FALSE, echo=FALSE, message=FALSE}
#Edit results in python and annotate them and add files back here
cindex_results_sum_sarc_grp_tmr <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/aneuploidies_AP.tsv', sep = '\t', header = TRUE, check.names = FALSE)

rownames(cindex_results_sum_sarc_grp_tmr) <- cindex_results_sum_sarc_grp_tmr$Sample.ID
cindex_results_sum_sarc_grp_tmr$Sample.ID <- NULL

cindex_results_sum_sarc_grp_tmr_meta <- read.table('/Users/aliciapliego/Projects/HRDsarcoma/data/cindex/aneuploidies_AP_meta.tsv', sep = '\t', header = TRUE, check.names = FALSE)

cindex_results_sum_sarc_grp_scaled = scale(cindex_results_sum_sarc_grp_tmr)
```

```{r , include=FALSE, echo=FALSE, message=FALSE}
library(dplyr)
colors <- c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C", "#FB9A99", "#E31A1C", "#FDBF6F", "#FF7F00" ,"#CAB2D6", "#6A3D9A" ,"#FFFF99", "#B15928")

Tumor_type = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT')
names(colors) <- Tumor_type

colors_df <- as.data.frame(colors)
colors_df$Tumor_type <- rownames(colors_df)
colors_tumor <- inner_join(colors_df,cindex_results_sum_sarc_grp_tmr_meta, by = "Tumor_type")

hrdcolors <- c("#EEA236FF","#46B8DAFF")
names(hrdcolors) <- c("High","Low")
hrdcolors_df <- as.data.frame(hrdcolors)
hrdcolors_df$HRDscore <- rownames(hrdcolors_df)

colors_tumor_hrd <- inner_join(colors_tumor,hrdcolors_df, by = "HRDscore")
#rownames(colors_tumor_hrd) <- colors_tumor_hrd$Tumor_type

list_tumor_colors <- c(colors_tumor_hrd$colors)
names(list_tumor_colors) <- colors_tumor_hrd$Tumor_type

list_hrd_colors <- c(colors_tumor_hrd$hrdcolors)
names(list_hrd_colors) <- colors_tumor_hrd$HRDscore
```

### Heatmap with boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- HeatmapAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_scaled), axis = TRUE))

Heatmap(t(cindex_results_sum_sarc_grp_scaled), 
        name = "CINscore", #title of legend
        column_title = "TCGA Aneuploidies", row_title = "Chromosome",
        cluster_columns = TRUE,
        cluster_rows =   FALSE,
        top_annotation = ha,bottom_annotation = ha_boxplot,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

### Heatmap without boxplot

```{r , echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}

library(ComplexHeatmap)


ha <- rowAnnotation(df = cindex_results_sum_sarc_grp_tmr_meta,
  col = list(Tumor_type = list_tumor_colors, 
             HRDscore = list_hrd_colors))

#ha_boxplot = HeatmapAnnotation(boxplot = anno_boxplot(t(cindex_results_sum_sarc_grp_tmr), axis = TRUE))

Heatmap(cindex_results_sum_sarc_grp_scaled, 
        name = "CINscore", #title of legend
        column_title = "TCGA Aneuploidies", row_title = "",
        cluster_columns = FALSE,
        cluster_rows =   FALSE,
        right_annotation = ha,
        row_names_gp = gpar(fontsize = 7) # Text size for row names
        ) 

#draw(ht, padding = unit(c(4, 2, 2, 2), "mm"))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width= 7, fig.height = 7, fig.align='center'}
library(reshape)
cindex_results_sum_sarc_grp_tmr2 <- as.data.frame(cindex_results_sum_sarc_grp_tmr)
cindex_results_sum_sarc_grp_tmr2$HRDscore <- cindex_results_sum_sarc_grp_tmr_meta$HRDscore
cindex_results_sum_sarc_grp_tmr2$Tumor_type <- cindex_results_sum_sarc_grp_tmr_meta$Tumor_type
mdata <- melt(cindex_results_sum_sarc_grp_tmr2, id=c("HRDscore","Tumor_type"))
mdata$variable <- NULL

fig <- plot_ly(mdata, x =~Tumor_type, y = ~value, color = ~HRDscore,type = "box", notched=TRUE) %>%
layout(boxmode= 'group',
     yaxis = list(range=c(-0.2,0.6), title = "Aneuploidies"),
     xaxis = list(title = "",
     categoryorder = "array",
     categoryarray = c('HGSOC',
                         'TNBC',
                         'CRC',
                         'UPS',
                         'MFS',
                         'OS',
                         'uLMS',
                         'MPNST',
                         'LMS',
                         'ddLPS',
                         'SS',
                         'DT'), tickangle = -45)
)

fig
```